Maintenance planning on French military aircraft operations

### 2018-02-16 R/roadef_presentation/roadef_presentation.Rmd
new version of ppt presented to Olga friday. Need to still take out many slides.

---
title: "Maintenance planning on French military aircraft operations"
author: "Franco Peschiera, Alain Haït, Olga Battaïa, Nicolas Dupin"
date: "February 14, 2018"
output: 
  beamer_presentation:
    theme: "Madrid"
    toc: true
    slide_level: 2
    incremental: yes
    fig_height: 4
  slidy_presentation:
    css: ./../../css/baobab_MH.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
nocite: '@*'
bibliography: MFMP.bib
---

@@

@@

## Problem

**Informally**:

@@

## Example

@@

## Problem

**Formally**:

@@

## State of the art

@@

@@

## Model: parameters

(Only **main parameters** are shown).

@@

## Model: parameters (2)

(**secondary parameters**).

@@

## Model: constraints (1)

@@

@@

## Model: constraints (2)

@@

## Model: constraints (3)

@@

## Model: constraints (4)

Visualization of each constraints for one resource.

## Results

@@

## Next steps

@@

## References

>>>>

---
title: "Maintenance planning on French military aircraft operations"
author: "Franco Peschiera, Alain Haït, Olga Battaïa, Nicolas Dupin"
date: "February 14, 2018"
output: 
  beamer_presentation:
    theme: "Madrid"
    toc: true
    slide_level: 2
    incremental: yes
    fig_height: 4
  slidy_presentation:
    css: ./../../css/baobab_MH.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    slide_level: 2
    toc: true
nocite: '@*'
bibliography: MFMP.bib
---

@@

# Introduction

@@

# Problem

## Problem (informally)

@@

## Problem (example)

@@

## Problem (formally)

@@

# State of the art

## State of the art (1)

@@

# Model

@@

## Model: main parameters

@@

## Model: more parameters

@@

## Model: main constraints

Requirements per task:
```{r out.width="250px", echo=FALSE}
knitr::include_graphics("./../../img/tasks_gantt.png")
```
\pause

Max maintenances:
```{r out.width="150px", echo=FALSE}
knitr::include_graphics("./../../img/num-maintenances.png")
```

## Model: main constraints

@@

\pause

@@

## Model: flow constraints

Visualization of accumulated time constraints for one resource.

## Model: flow constraints

@@

## Model: flow constraints

@@

# Results

## Experiments

@@

# Next steps
## Next steps

@@

# References
## References

<!-- \bibliographystyle{dcu} -->
<!-- \bibliography{./../biblio/MFMP} -->
